Formulating Regional Typologies

### 2023-11-01 regional_typologies.qmd
Update regional_typologies.qmd

```{r Map}
#| warning: false
#| message: false
```

### K-means cluster

```{r K-means cluster}
#| warning: false
#| message: false
```
:::

@@

```{r Map}
#| warning: false
#| message: false
library(plotly)
library(leaflet)
library(sf)
library(dplyr)

@@

![](image/5cluster.png){height="450" fig-align="center"}

@@

-   Closest to plantations, forests, and deforestation sites.

>>>>

```{r PCA Summary}
#| warning: false
#| message: false
readr::read_csv("data/pca_summary.csv") |> 
  gt()|>
  tab_header(
    title = "Principal Component Analysis Summary",
    subtitle = "Importance of components") |> 
    opt_align_table_header(align = "left")
```

---
#### Loadings Interpretation
**PC1: Predominantly Demography & Disaster Risk**
![](image/loadings PC1.png)

**PC2: Predominantly Climate Features**
![](image/loadings PC2.png)

**PC3: Predominantly Distance Features**
![](image/loadings PC3.png)

### K-means cluster
#### The first three principal components, colored by cluster
```{r K-means cluster}
#| warning: false
#| message: false
library(plotly)
library(leaflet)
library(sf)
library(dplyr)

plot_data <- readr::read_csv("data/cluster_3d_viz.csv") |> dplyr::mutate(cluster = as.factor(cluster))
# Create the 3D scatter plot
plot_3d <- plot_ly(
  data = plot_data,
  x = ~ PC1,
  y = ~ PC2,
  z = ~ PC3,
  color = ~ cluster,
  type = "scatter3d",
  text = ~ paste("Kab./Kota:", nmkab, "<br>Kecamatan:", nmkec),
  mode = "markers"
) 
# Show the plot
plot_3d

```
#### Cluster Validation
::: {layout-ncol=2}

![The "elbow" of the plot is the point where adding more clusters doesn't provide much better fit to the data.](image/elbow_method.png)

![A silhouette plot closer to +1 indicates good clustering, while values closer to 0 or negative values suggest overlapping or poor clustering](image/shilloutte_analysis.png)
:::
:::

@@

```{r Map}
#| warning: false
#| message: false

@@

@@

-   Close to plantations, forests, and deforestation sites.
